%-------------------------
% Resume Template
% Author : Orest Tokovenko
% Github : https://github.com/oresttokovenko
% License : MIT
% Type: General Non-Technical
%------------------------

%-------------------------------------------------------------------------------
%                Document & Class
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{resume_config}
% Set the font and formatting for the entire document
\renewcommand{\sfdefault}{phv}
\usepackage{lmodern} % Use the Latin Modern font
\usepackage{hyperref}
\hypersetup{breaklinks=true}
% NOTE: <- font size adjustment is available in the resume_config.cls file on the left hand side. ex. \LoadClass[#pt]{article} where # is 10, 11 or 12

% NOTE: If you need to adjust the space between any two lines, use this function: \vspace{#pt} where # is your number. ex. \vspace{-5pt} decreases the space between lines

%-------------------------------------------------------------------------------
%                Resume Starts Here
%-------------------------------------------------------------------------------

\begin{document}
\Header{AYUSH SAXENA}{2}{ayushsaxena.official01@gmail.com}{ayush-saxena-a766b418b}{Ayush1906saxena}








%-------------------------------------------------------------------------------
%                Work Experience
%-------------------------------------------------------------------------------

\section{Skills}
\begin{SkillsList}
    \item \textbf{Programming Languages:} Java, Python, JavaScript \\
    \item \textbf{Framework and Tools:} \textbf{Oracle SQL(rdbms)}, MongoDB(nosql), Spring5, Hibernate, NextJS, Express, Git, \textbf{Docker, Kubernetes}  \\
    \item \textbf{Core Subjects:} Operating System, Database Management System(DBMS), OOPS, Linux, Software Engineering
    \item \textbf{Problem Solving:} \textbf{Data Structures, Algorithms}, Backend Development, Data Analytics, Business Intelligence, API, Web Services(SOAP and REST), \textbf{DevOps}, \textbf{CICD using Jenkins/Jules}, \textbf{AWS Solutions Architect}.
    \item \textbf{Soft Skills:} Multi-tasking, Leading projects, Agile, Ability to pick up new languages and deliver tasks, Good Communication skills
    % Add more skills as needed
\end{SkillsList}

\section{Work Experience}

\WorkExperience
    {JPMorgan Chase \& Co. : \textbf{Software Engineer 1}} % job title
    {} % company name
    {Feb 2023 -- Present} % beginning and end of employment. If currently employed write " - Present"
    {} % city, country of employment
    {
        \item Engineered the full-scale migration of the LOANIQ application from an on-premises infrastructure to the \textbf{Gaia Kubernetes Platform (GKP)} in the NA data center, \textbf{containerizing key vendor packages and microservices using Docker}. Automated multi-environment \textbf{infrastructure provisioning with Terraform}, implementing cluster autoscaling, \textbf{load balancing} across multiple Kubernetes clusters, and ensuring fault tolerance, performance optimization, and minimal downtime during the transition.
        \item Designed and deployed a \textbf{custom health check UI} as a web application hosted on Kubernetes, providing real-time visibility into the health and status of development, UAT, and production environments. This UI \textbf{consolidated environment monitoring into a single interface}, improving operational efficiency and proactive issue resolution.
        \item Orchestrated a \textbf{seamless database migration from DBaaS to Gaia Oracle Service (GOS)}, leveraging \textbf{Oracle GoldenGate} for real-time cross-schema replication between OLTP and reporting databases, ensuring data integrity and zero downtime during the migration process.
        \item \textbf{Consolidated over 300 LOANIQ interfaces} into a single repository leading to just one pipeline for deploying the entire project. This initiative taught me in-depth skills of \textbf{Jules}. Also implemented an aggregator pipeline for other interfaces. This initiative streamlined the deployment process and also \textbf{reduced deployment time by 90\%}. Utilized control-m for batch testing.
        \item Successfully \textbf{performed Database schema split} for LOANIQ by splitting a very complex and cluttered oracle database into OLTP and OLAP. This initiative reduced query \textbf{processing time for OLTP jobs by an impressive 90\%} and helped logically differentiate JPMC related jobs with Finastra  batch Jobs. This initiative made our modernization team ready for \textbf{migration to GOS(Gaia Oracle) database} further advancing our systems.
    } 
\vspace{-10pt}
\section{Projects}

\WorkExperience
    {\href{https://github.com/Ayush1906saxena/sfg-pet-clinic}{Dog Clinic Application}} % job title

    {9th Jun 2022 -- 10th Jun 2022} % beginning and end of employment. If currently employed write " - Present"
    
    {
        \item Created a pet clinic web app using \textbf{Spring Boot and Hibernate}, for efficient data management.
        \item Developed \textbf{RESTful} services with Spring MVC, ensuring sub-50 ms response times for seamless front-end and back-end communication.
        \item  Managed data persistence with \textbf{Spring Data JPA and Hibernate}, achieving sub-5ms average database query response times for entity management.
        \item Employed \textbf{Thymeleaf} for dynamic HTML templates, resulting in a 20\% reduction in page load times, simplifying the presentation layer.
        \item  Executed comprehensive unit and integration testing with a focus on end-to-end scenarios, achieving a \textbf{code coverage of 90\%} for reliable functionality.
    } 
\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Certifications
%-------------------------------------------------------------------------------

\section*{Certifications}
\begin{tabular}{p{0.75\textwidth} r}
  \Certification{\href{https://www.credly.com/badges/206c77db-681a-45dd-a19b-a7a86991c1e6/linked_in_profile}{AWS Certified Cloud Practitioner}}{10th Sept 2023 – 20th Sept 2023} \\
  \Certification{\href{https://www.credly.com/badges/c8578ec9-3270-467f-a7a9-ce08911cc0ef?source=linked_in_profile}{Google Data Analytics Professional Certificate}}{20th Oct 2021 – 24th Dec 2021} \\
  \Certification{\href{}{Java Professional Summer Training}}{17th Jun 2020 – 28th Jul 2020} \\
\end{tabular}


\vspace{-7pt}
%-------------------------------------------------------------------------------
%                Education
%-------------------------------------------------------------------------------

\section{Education}

\EducationExperience
    {Vellore Institute of Technology} % school name
    {B.Tech. Computer Science and Engineering} % credential name
    {Jun 2023} % date of graduation
    {CGPA: 8.72} % city, country of school

\vspace{-7pt}
%-------------------------------------------------------------------------------
%                Skills
%-------------------------------------------------------------------------------



\section{Coding Experience}
\begin{SkillsList}
    \item \textbf{Leetcode:} Experienced in a variety of Data structures and Algorithms, having solved 650+ problems. \\
    % Add more skills as needed
\end{SkillsList}

\end{document}

%-------------------------------------------------------------------------------
%                Resume Ends Here
%-------------------------------------------------------------------------------
